Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-19 article.tex
further edits to intro

However, even in light of it's phenomenally far-reaching success in almost all areas of modern science and engineering, classical computation still
has its limitations. When it comes to simulating microscopic systems, classical techniques require significant computational overhead which scales to
unreasonable proportions with increasing system size. In quantum computational chemistry simulations, each subatomic orbital and their interactions
needs to be considered to achieve an accurate and realistic simulation of the microscopic system. Since the state of one orbital can be affected by
all of the others, an exponential number of states in the basis of molecular orbitals needs to be accounted for. This is what we call ‘many body’ problems.
No matter how far apart two orbitals are, their quantum states cannot be described independently, the repeated interactions between particles create
quantum correlations, this phenomenon is known as entanglement.

@@

The amount of information needed to describe interactions in a quantum system would quickly fill up the memory in a classical computer, instead,
a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits to information storage and computation
\cite{trabesinger2012quantum}. Since the classical storage unit ‘bit’ is binary system based on strings of 0s and 1s, but quantum computer encodes
 them into two distinguishable quantum states, and one qubit can represent multiple states once by quantum phenomenon ‘superposition’. Similarly,
 if we perform a searching algorithm on a classical string, the enumerate steps would be the number of bits within this string. Comparably, our
 processing step will reduce a lot more as we only need to compute once in a quantum processor.

>>>>

However, even in light of it's phenomenally far-reaching success in almost all areas of modern science and engineering, classical computation still
has its limitations. When it comes to simulating microscopic systems, classical techniques require significant computational overhead which scales to
unreasonable proportions with increasing system size. In quantum computational chemistry simulations, each subatomic orbital and their interactions
needs to be considered to achieve an accurate and realistic simulation of the microscopic system. Since the state of one orbital can be affected by
all of the others, an exponential number of states in the basis of molecular orbitals needs to be accounted for. Problems of this type are classified
to be ‘many-body’ problems. No matter how far apart two orbitals are, their quantum states cannot be described independently, the repeated interactions between particles create
quantum correlations, this phenomenon is known as entanglement.

@@

The amount of information needed to describe interactions in a quantum system would quickly fill up the memory of a classical computer, instead,
a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits, for information storage and computation
\cite{trabesinger2012quantum}. Since the classical storage unit ‘bit’ is binary system based on strings of 0s and 1s, but a quantum computer would
encode them into two distinguishable quantum states, and one qubit can represent multiple states at once in the form of the quantum phenomenon of
‘superposition’. Similarly, if we perform a search algorithm on a classical string, the enumerate steps would be the number of bits within this
string. Comparably, our processing step will reduce a lot more as we only need to compute once in a quantum processor.
